---
title: "Penguin Body Size by Species"
author: "Maryam"
date: "2026-09-24"
---

## Introduction

In this analysis we explore whether body mass and flipper length differ
across the three penguin species: Adelie, Chinstrap, and Gentoo.

Data: [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/),
Palmer Station Antarctica LTER. Available under a CC0 license.

```{r}
#| label: setup
#| message: false
#| warning: false

library(palmerpenguins)
library(dplyr)
```

## Preparing the data

We first load the dataset and remove rows with missing values.

```{r}
#| label: clean-data

penguins_clean <- penguins |>
  filter(!is.na(body_mass_g), !is.na(flipper_length_mm), !is.na(species))

head(penguins_clean)
```

## Summary statistics by species

We compute the mean and standard deviation of body mass and flipper length
for each species.

```{r}
#| label: summary-stats

penguins_summary <- penguins_clean |>
  group_by(species) |>
  summarize(
    mean_body_mass = mean(body_mass_g),
    sd_body_mass = sd(body_mass_g),
    mean_flipper_length = mean(flipper_length_mm),
    n = n()
  )

penguins_summary
```

From this table, we can see that Gentoo penguins are noticeably heavier
than the other two species.

## Conclusion

Based on the table and figure above, Gentoo penguins are clearly heavier
than the other two species, while Adelie and Chinstrap have more similar
body mass distributions.